Potential of I/O Aware Workflows in Climate and Weather

### 2020-05-22 paper.tex
Changed title, added one sentence about performance model.

\title{Potential of I/O-Aware Workflows in Climate and Weather}

@@

The vision proposed here is built on the belief that workflows composed of data, computing, and communication-intensive tasks should drive interfaces and hardware configurations to best support the programming models.
When delivered, this work will increase the opportunity for smarter scheduling of computing by considering storage in heterogeneous storage systems.

\keywords{workflow, climate, weather, heterogeneous storage, data-driven}
\end{abstract}

>>>>

\title{Potential of I/O Aware Workflows in Climate and Weather}

@@

The vision proposed here is built on the belief that workflows composed of data, computing, and communication-intensive tasks should drive interfaces and hardware configurations to best support the programming models.
When delivered, this work will increase the opportunity for smarter scheduling of computing by considering storage in heterogeneous storage systems.
We illustrate the performance-impact on an example workload using a model built on measured performance data at DKRZ.

\keywords{workflow, heterogeneous storage, data-driven, climate/weather}
\end{abstract}
